Differential Expression - MSSM-Penn-Pitt - ACC DLPFC - Dx.Tissue

### 2020-05-21 MSSM-Penn-Pitt_DE_DxTissue.Rmd
supress warning and drop colinear vars

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))

```

`r formula`

>>>>

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
# remove RIN2 as RIN and RIN2 are highly correlated
adjust.covars <- c("Dx.Tissue", "ageOfDeath", "EV.1", "PMI", "EV.4","EV.2","RIN", "EV.3", "EV.5", "IntronicRate")
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```
#drop redundancy - RIN2 or RIN
#use canCorPairs() to test colinearity, don't want var of interest to be correlated
#leave out random effects
`r formula`
